---
title: "Workflow for installing and using retrieveR"
author: "John Brandt"
date: "8/16/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Info

This vignette walks the user through applying the neural embedding NLP approach to a novel set of PDF documents. We use a sample corpus of eight peer-reviewed academic journal articles about restoration. 


## Installation instructions

R can be downloaded from [this link](https://cran.r-project.org/bin/windows/base/). Once it is downloaded, open up the 32-bit version (i386, as WRI computers only seem to have 32-bit version of Java). Then, you can proceed to installing the package by running the following lines of code. Copy and paste them one at a time and press enter.

```{r, eval = F}
install.packages("devtools")
library(devtools)
install_github("wri/retrieveR")
```

## Downloading data

Next, we load up the package into R using `library`. Depending on your operating system, you then need to run either `install_mac` or `install_windows` - these functions will get the Java dependencies to extract text from images, as well as install the necessary components to run neural networks.

Finally, the `download_example` function will download the example PDFs.

```{r, eval=F}
library(retrieveR)
install_mac()
install_windows()
download_example()
```

## Prepping documents for querying

The `prep_documents` function will strip text from the PDFs, clean up the results, and calculate neural weights. These can be turned off by specifying `ocr = F`, `clean = F`, or `weights = F`. The function takes a path to the folder of documents - in this case they are stored in a folder called `pdfs`. This pathing is local to the directory that R is running in - this can be printed with `getwd()` and changed with `setwd()`. 

```{r, warning = F, message = F, eval=F}
corpus <- prep_documents("pdfs")
```

## Querying documents for paragraphs related to land tenure

The `create_report` function takes the following arguments:

1. query: Query phrase within quotations.
2. data: name that the output of `prep_documents` is stored to.


```{r, eval = F}
create_report(query = "food water waste wastewater reuse", data = corpus)
```

```{r, warning = F, message = F, echo = F, eval=F}
create_report(query="land tenure", data = corpus, interactive = F, thresh = 0.51)
```

## Results

The results of the `create_report` function are stored in an html file in the working directory. I have included the results within this file for ease of example. 

```{r, echo=FALSE, warning = F, message = F}
htmltools::includeHTML("land_tenure.html")
```
